Molecular dynamics simulation of synchronization in driven particles

### 2021-01-10 manuscript/manuscript_ajp_2020.tex
do next, fig. 3~

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{landscape.pdf}
\caption{
  Schematic of the simulation
  of a single particle
  driven across a washboard potential
  energy landscape.
  The period of the landscape, $\lambda = L/N_p$ 
  where $N_p = 3$, is marked in red.
  The force due to the landscape %$\vec{F}^l$
  is calculated from the gradient of the potential
  energy 
  $\vec{F}^l = -\nabla U(\vec{r})$.
  (a) View of the $x-y$ plane. %of the simulation
  The time-dependent applied driving force $\vec{F}^D$
  is parallel to the y-axis.
  The landscape is shown with a contour plot,
  with maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is shown in the region between minima and maxima
  subject to competing forces due to the landscape and applied driving force.
  (b) The potential energy function
  along the y-axis $U_l(y)$,
  The particle in (a) is shown at the same $y-$position,
  where the magnitude of force $\vec{F}^l$ is calculated as the slope of this function,
  directed along the $y-$direction in panel (a).
  }
\label{fig:landscape0}
\end{figure}
\end{center}

 Particles are subject an external time-dependent driving force
$\vec{F}_{D}(t)$
applied parallel to the y-direction.
We model this force as
\begin{equation}
  \vec{F}^{D}(t) = [F^{DC} + F^{AC} \sin(\omega t)] \hat{y},
    \label{eq:drive}
\end{equation}
with modifiable parameters including
a constant component $F^{DC}$,
and a time dependent component with amplitude $F^{AC}$
and frequency $\omega = 2 \pi f$.
%in the positive $y-$direction.
%but it may 
%be zero or negative depending the the parameters and time.
When $F^{DC}$ is non-zero,  
%In several simulations
we slowly increase 
$F^{DC}$ from zero
to avoid transient behavior
by ensuring the particle is subject to a smoothly varying force.
We illustrate the increase
of $F^{DC}$ in Fig.~\ref{fig:0}(a).

%because
The inertia of 
small particles is greatly reduced by interactions
with fluid particles \cite{Purcell1977}.
Our model 
colloids are overdamped
-- i.e. suspended in a continuous viscous fluid
that dissipates energy at a rate such 
that the particles do not accelerate.
%that greatly impedes their motions.
Energy dissipation from the fluid is modeled
with a frictional force on particle with velocity $\vec{v}_i$
%that removes energy from
%the particles,
%which we model as
$\vec{F}^{drag}_i = -\eta \vec{v}_i$
%proportional to the particle velocity 
with a friction coefficient $\eta$
proportional to the fluid viscosity.
We discuss friction models for
spheres moving through fluids in 
Section~\ref{sec:problems} Exercise~\ref{ex:reynolds}. %for more information
%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
Newton's second law for an individual particle
%$m \vec{a}_i = \sum \vec{F}$
is simplified
by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The overdamped equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{D}(t).
    \label{eq:motion}
\end{equation}
with  $\eta = 1$.  
%which we describe in more detail in Table~\ref{tab:1}
%and Exercise~\ref{ex:reynolds}.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:n2l}
we invite the reader to confirm this result.

@@

%\section{Results}
%\label{sec:results}
% We demonstrate how a single particle (Sec.~\ref{sec:one})
% and many particles
% move (Sec.~\ref{sec:sync})
% in response to this applied force in a variety of environments.
% In Sec.~\ref{sec:kink} we set $F^{DC}$
% to zero and track the motion
% of a high density area of a particle chain
% (i.e. kink dynamics).
 %The driving force does add energy into the system, and some of it is lost.
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:one}

A single particle on this landscape
responds to the applied driving force
by synchronizing its motion across the landscape maxima 
to the periodic pattern of 
applied driving force.
In Fig.~\ref{fig:0} we
show the relationship between the applied force and particle
position % as a function of time.
for 
%We drive
a single particle driven across a periodic landscape. 
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
\end{equation}
where the force is scaled with parameter $A_{p} = 0.1$ force units 
%in simulation units for force. % $E_0/a_0$.
%The substrate is described in 
%\begin{equation}
%  \label{eq:landscape_potential}
%  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
%\end{equation}
with $N_p=20$ %troughs in the landscape
and spatial period $\lambda = 1.825 a_0$.
%
In Fig.~\ref{fig:0}(a)
we plot the applied driving force defined in Eq.~\ref{eq:drive}
as a function of time.
The time independent constants are 
$F^{AC}=0.05$ and $f=0.01$ cycles per time unit.
The temporal period of the driving force is
$T = 1/f = 100$.
To avoid transient oscillations at early times, 
the dc driving force is initially zero   
and 
slowly increased %$F^{DC}$.
at a rate of $\Delta F^{DC} = 0.01$ every $\Delta t = 4000$ integer timesteps 
to the constant value $F^{DC}=0.1$.
In Fig.~\ref{fig:0}(a) we plot $F^{DC}$
in blue to show the increase in 
$F^{DC}$ for the first $40$ time units.
In orange we show 
the combined ac and dc drive $F^D(t)$,
where 
the magnitude of the ac applied force is initially zero.
%since $\sin{(0)}=0$.
The vertical dashed lines in panels (a) and (b) coincide
with the condition $\sin{(\omega t)} = 1$,
where the applied force is maximum once $F^{DC}$ has become constant.

%with the initial driving force at is minimum value 
%$F^D(0) = F^{DC}$.

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by the spatial period of the potential %washboard as
$\lambda$.
The initial particle position is $y=0$,
where the landscape force is minimum $F^l = 0$.
The horizontal dashed lines
coincide with the condition the substrate force is
minimum 
$\sin{(\pi y / \lambda)} = 1 $, so $F^l = -A_p$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
The crossing of the particle position $y$
with the horizontal and vertical lines
indicates the synchronization
of the driving force with the lattice position of the particle,
where driving force is maximum positive when the
force on the particle from the landscape is maximum negative.
It can be shown this synchronization
occurs for any initial position of $y$.
({\it exercise to student})

The slope of $y/\lambda$
is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.
Here 
the particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
with 
the average velocity 
$\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%The average velocity $\bar{v}_y$
%is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
%over the period of the driving force.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single DC case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^D(t)$ (orange) in Eq.~\ref{eq:drive}
  where the parameter $F^{DC}$ (blue) is slowly increased from zero
  to a constant value
  as described in the text.  (b) 
  The $y-$position of the driven particle
  as a function of time %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  }
\label{fig:0}
\end{figure}
\end{center}

The ratio of $F^{AC}/F^{DC}$ and the barrier height $A_p$
control the rate and length of the particle hops
forward and backward in the landscape.
When $F^{AC}/F^{DC} > 1$
and $F^{DC} - F^{AC} > A_p$ the particle
moves in the negative y-direction 
during part of the cycle.
To explore the possible hopping patterns,
we sweep through a range of $F^{DC}$ for fixed $F^{AC}$ and $A_p$,
as shown in Fig.~\ref{fig:1}(b).
We keep $F^{DC}$ constant
for $\Delta t = 10^4$ timesteps
and 
sample the average velocity $\langle v_y \rangle $ 
as a function of $F^{DC}$.

We perform this sweep for several values
of $F^{AC}$ including the limiting case that the applied force
is a constant value.
When $F^{AC} = 0$, no steps appear
in the $\langle v_y \rangle $ vs $F^{DC}$ curve.

Synchronization
of the driving force with the landscape,
despite the overall magnitude
of $F^{DC}$.

@@

The particle 
achieves a variety of oscillation modes as a function of $F^{DC}$.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\bar{v}_{y}$
over a range of driving forces $F^{DC}$.
We illustrate mode-locking in 
the velocity-force plot in Fig.~\ref{fig:1}(b).
Here $\langle v_{y} \rangle$ is increasing in non-uniform steps,
with a quantized height of
$\langle v_{y} \rangle = n \lambda f$,
where $n$ is an integer.  
%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
%of the landscape,
%and $f = 0.01$ cycles per time unit.

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single}
\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{DC}$.}
\label{fig:1}
\end{figure}
\end{center}

@@

When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion. A driven particle can exhibit mode locking with a well-chosen AC drive and frequency. In the attached movie, Figure2.mp4, we show the complex dynamics of mode locking, where the driven particle leap-frogs past the other particles.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{twenty}
\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel. The landscape is colored as in Fig.~\ref{fig1}(a). \textbf{(b)} Average $\bar{v}_{y}$ versus $F^{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
\label{fig:2}
\end{figure}
\end{center}

\section{Kinked system}
\label{sec:kink}	% You can label sections for reference
We confine $N$ particles to $N-1$ troughs to create a
local high density region.
$F^{DC}/F^{AC} = 1$ [CHECK!]

@@

\item Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on a particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$
  The addition of a dissipative force in a dynamical model
  on a colloid is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \eta \vec{v}_i$
  where $\eta$ is the drag coefficient.
  Demonstrate
  the ratio of $m/\eta$ has units of time, 
  %This ratio of the acceleration coefficient $m$
  %to the drag coefficient $\eta$
  %is
  known as the momentum relaxation time.
  The momentum relaxation time is 
  known to be small for
  particles with low Reynolds numbers,
  indivating 
  a regime in which the acceleration term can be ignored
  entirely.
  Demonstrate that a particle confined to a landscape exerting force
  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
  can be modeled with the equation of motion described in 
  Eq.~\ref{eq:motion}. 
  \label{ex:n2l}

@@

%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied AC forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves.

>>>>

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{landscape.pdf}
\caption{
  Schematic of the simulation
  of a single particle
  driven across a washboard potential
  energy landscape.
  The period of the landscape, $\lambda = L/N_p$ 
  where $N_p = 3$, is marked in red.
  The force due to the landscape %$\vec{F}^l$
  is calculated from the gradient of the potential
  energy 
  $\vec{F}^l = -\nabla U(\vec{r})$.
  (a) View of the $x-y$ plane. %of the simulation
  The time-dependent applied driving force $\vec{F}^d$
  is parallel to the y-axis.
  The landscape is shown with a contour plot,
  with maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is shown in the region between minima and maxima
  subject to competing forces due to the landscape and applied driving force.
  (b) The potential energy function
  along the y-axis $U_l(y)$,
  The particle in (a) is shown at the same $y-$position,
  where the magnitude of force $\vec{F}^l$ is calculated as the slope of this function,
  directed along the $y-$direction in panel (a).
  }
\label{fig:landscape0}
\end{figure}
\end{center}

 Particles are subject an external time-dependent driving force
$\vec{F}_{D}(t)$
applied parallel to the y-direction.
We model this force as
\begin{equation}
  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
    \label{eq:drive}
\end{equation}
with modifiable parameters including
a constant component $F^{dc}$,
and a time dependent component with amplitude $F^{ac}$
and frequency $\omega = 2 \pi f$.
%in the positive $y-$direction.
%but it may 
%be zero or negative depending the the parameters and time.
When $F^{dc}$ is non-zero,  
%In several simulations
we slowly increase 
$F^{dc}$ from zero
to avoid transient behavior
by ensuring the particle is subject to a smoothly varying force.
We illustrate the increase
of $F^{dc}$ in Fig.~\ref{fig:0}(a).

%because
The inertia of 
small particles is greatly reduced by interactions
with fluid particles \cite{Purcell1977}.
Our model 
colloids are overdamped
-- i.e. suspended in a continuous viscous fluid
that dissipates energy at a rate such 
that the particles do not accelerate.
%that greatly impedes their motions.
Energy dissipation from the fluid is modeled
with a frictional force on particle with velocity $\vec{v}_i$
%that removes energy from
%the particles,
%which we model as
$\vec{F}^{drag}_i = -\eta \vec{v}_i$
%proportional to the particle velocity 
with a friction coefficient $\eta$
proportional to the fluid viscosity.
We discuss friction models for
spheres moving through fluids in 
Section~\ref{sec:problems} Exercise~\ref{ex:reynolds}. %for more information
%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
Newton's second law for an individual particle
%$m \vec{a}_i = \sum \vec{F}$
is simplified
by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The overdamped equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{d}(t).
    \label{eq:motion}
\end{equation}
with  $\eta = 1$.  
%which we describe in more detail in Table~\ref{tab:1}
%and Exercise~\ref{ex:reynolds}.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:n2l}
we invite the reader to confirm this result.

@@

%\section{Results}
%\label{sec:results}
% We demonstrate how a single particle (Sec.~\ref{sec:one})
% and many particles
% move (Sec.~\ref{sec:sync})
% in response to this applied force in a variety of environments.
% In Sec.~\ref{sec:kink} we set $F^{dc}$
% to zero and track the motion
% of a high density area of a particle chain
% (i.e. kink dynamics).
 %The driving force does add energy into the system, and some of it is lost.
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:one}

A single particle %on this landscape
responds to the applied driving force
by synchronizing its motion across the landscape %maxima 
to the periodic pattern of 
applied driving force.
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
\end{equation}
where the force is scaled with parameter $A_{p}$.
In this section, we fix the landscape parameters
to $A_{p} = 0.1$ force units
with $N_p=20$ minima in the landscape
corresponding to a spatial period $\lambda = 1.825 a_0$.

In Fig.~\ref{fig:0} 
a single driven particle adjusts
its motion so the particle traverses
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^d(t)$.
%
In Fig.~\ref{fig:0}(a)
we plot $F^d(t)$ defined in Eq.~\ref{eq:drive}.
%as a function of time.
The time independent constants are 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit.
The temporal period of the driving force is
$T = 1/f = 100$ time units.
To avoid transient oscillations at early times, 
the dc driving force is initially zero   
and 
slowly increased %$F^{dc}$.
at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  
to the constant value $F^{dc}=0.1$.
In Fig.~\ref{fig:0}(a) we plot $F^{dc}$
in blue to show the increase in 
$F^{dc}$ for the first $40$ time units
In orange we show 
the combined ac and dc drive $F^d(t)$ 
when the magnitude of the ac applied force is initially zero.
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
(i.e. $\sin{(\omega t)} = 1$).

%with the initial driving force at is minimum value 
%$F^d(0) = F^{dc}$.

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by $\lambda$, the spatial period of the potential.
The initial particle position is $y = 1$,
where the landscape force is negative $F^l < 0$,
causing the particle to move into
a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
and the motion of the particle
becomes locked to the driving period $T$.
The horizontal dashed lines
coincide with the condition the substrate force is
minimum $F^l = -A_p$ 
(i.e. $\sin{(\pi y / \lambda)} = 1$).
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
Once the particle motion
coincides with the applied drive, 
the particle position $y$
crosses the intersection of
the horizontal and vertical lines.
This indicates 
the driving force is maximum positive when the
force on the particle from the landscape is maximum negative,
indicating synchronization.
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
We invite interested students to repeat this
simulation for any initial particle position %of $y$
and a range of simulation constants
to demonstrate that synchronization in this model
does not depend on a particular set of conditions.
%but is a direct consequence of the simplicity of the model.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^d(t)$ (orange) in Eq.~\ref{eq:drive}
  where the parameter $F^{dc}$ (blue) is slowly increased from zero
  to a constant value
  as described in the text.  (b) 
  The $y-$position of the driven particle
  as a function of time %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  }
\label{fig:0}
\end{figure}
\end{center}

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion.
If $A_p$ is large compared to the extrema of $F^{d}(t)$,
the particle is trapped in a single
minima so it oscillates back and forth with no net velocity.
When $F^d(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.
In Fig.~\ref{fig:0}
the particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
with 
the average velocity 
$\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%The average velocity $\bar{v}_y$
%is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
%over the period of the driving force.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1

The ratio of $F^{ac}$, $F^{dc}$ and the barrier height $A_p$
control the rate and length of the particle hops
forward and backward in the landscape.
When $F^{ac}/F^{dc} > 1$
and $F^{dc} - F^{ac} > A_p$ the particle
moves in the negative y-direction 
during part of the cycle.
To explore the possible hopping patterns,
we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$,
as shown in Fig.~\ref{fig:1}(b).
We keep $F^{dc}$ constant
for $\Delta t = 10^4$ timesteps
and 
sample the average velocity $\langle v_y \rangle $ 
as a function of $F^{dc}$.

We perform this sweep for several values
of $F^{ac}$ including the limiting case that the applied force
is a constant value.
When $F^{ac} = 0$, no steps appear
in the $\langle v_y \rangle $ vs $F^{dc}$ curve.

Synchronization
of the driving force with the landscape,
despite the overall magnitude
of $F^{dc}$.

@@

The particle 
achieves a variety of oscillation modes as a function of $F^{dc}$.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\bar{v}_{y}$
over a range of driving forces $F^{dc}$.
We illustrate mode-locking in 
the velocity-force plot in Fig.~\ref{fig:1}(b).
Here $\langle v_{y} \rangle$ is increasing in non-uniform steps,
with a quantized height of
$\langle v_{y} \rangle = n \lambda f$,
where $n$ is an integer.  
%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
%of the landscape,
%and $f = 0.01$ cycles per time unit.

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single}
\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{dc}$.}
\label{fig:1}
\end{figure}
\end{center}

@@

When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion. A driven particle can exhibit mode locking with a well-chosen ac drive and frequency. In the attached movie, Figure2.mp4, we show the complex dynamics of mode locking, where the driven particle leap-frogs past the other particles.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{twenty}
\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{ac}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel. The landscape is colored as in Fig.~\ref{fig1}(a). \textbf{(b)} Average $\bar{v}_{y}$ versus $F^{dc}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
\label{fig:2}
\end{figure}
\end{center}

\section{Kinked system}
\label{sec:kink}	% You can label sections for reference
We confine $N$ particles to $N-1$ troughs to create a
local high density region.
$F^{dc}/F^{ac} = 1$ [CHECK!]

@@

\item Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on a particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$
  The addition of a dissipative force in a dynamical model
  on a colloid is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \eta \vec{v}_i$
  where $\eta$ is the drag coefficient.
  Demonstrate
  the ratio of $m/\eta$ has units of time, 
  %This ratio of the acceleration coefficient $m$
  %to the drag coefficient $\eta$
  %is
  known as the momentum relaxation time.
  The momentum relaxation time is 
  known to be small for
  particles with low Reynolds numbers,
  indivating 
  a regime in which the acceleration term can be ignored
  entirely.
  Demonstrate that a particle confined to a landscape exerting force
  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
  can be modeled with the equation of motion described in 
  Eq.~\ref{eq:motion}. 
  \label{ex:n2l}

@@

%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves.
